Prefetching SPARQL query cacher

### 2016-05-26 dissertation/cache-proxy.tex
discuss the fail

\subsection{Planned evaluation}

@@

@@

>>>>

\subsection{Planned evaluation}\label{sec:planned}

@@

\subsection{Remedies for performance issues}\label{sec:discussfail}

One may raise the issue that it was a bad idea to begin with to use a
scripting language like Perl to write a query engine with performance
requirements. Indeed, that may be the case. However, generally
accepted practice is to first find the actual performance issues and
then optimise using a bridge to first and foremost the C family of
languages as needed. Importantly, with the width of the scope, I only
had some months to implement the query engine. This is not a software
engineering project, but given past industrial experience, it seems
unlikely that I could have achieved it within the allowed time frame
using older paradigms, such as the factory method pattern.

The profiling points out a clearly where large gains could be
made. First and foremost, parsing must be avoided, and that could be
avoided by ensuring that IRIs where canonicalised before they were
written to the cache, so that comparing them later would be a simple
string comparison. Secondly, the Redis data structure store could be
better exploited to store strings that could be used to construct  
literals and IRI objects without parsing.

However, since computing the join itself is too slow, it is not
necessarily a solution worth pursuing. The main motivation behind
caching hashes and arrays in Redis was to save space; since at least
one term would be bound in any cached pattern, it shouldn't be
necessary to insert more data into the cache. Since the performance of
doing the join is poor, this may not be justified. Instead, it may be
a better idea to use a conventional quad store for the cache. In that
case, the planner would require a simple modification so that triple
patterns are gathered into locally evaluated BGPs and remotely
evaluated BGPs as well as LDFs. To take full advantage of this
approach, SPARQL 1.1 \sparql{VALUES} would also need to be supported,
so that the local quad store could perform all join operations. To
this end, I wrote a rudimentary Virtuoso store driver for Attean, but
at that point, the project was overdue and needed to be concluded.

It seems likely that the project, with more time, could be brought to
the point where a the evaluation in Section~\ref{sec:planned} could be
applied, and new insight could be gained.

Thus, the main contribution from this project is the remarkable ease
with which it was implemented.

@@

%%  LocalWords:  canonicalised
